---
title: "5xfad_wt"
output: html_notebook
---

Analysis of NGS and proteomics data from 5xfad mouse brains - this analysis focuses only on the wt subset of the data

Load relevant libraries and import data:

```{r}
library("DESeq2")
library("ggplot2")
library("RColorBrewer")

setwd("E:/dev_workspace/5XFAD")

in_data_RNA <- read.csv("input/5XFAD_counts_unnorm.csv", header = T, stringsAsFactors=FALSE)

row.names(in_data_RNA) = in_data_RNA[,1]
raw_data_RNA <- in_data_RNA[-c(1:3)]
raw_data_RNA <- data.frame(raw_data_RNA)
head(raw_data_RNA)
```


```{r}
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
